Estimate Non-zero mode

### 2016-10-21 analysis/estimate_mode.Rmd
Revised	efron.fcr.Rmd.
Revised estimate_mode.Rmd.

```{r}
check_mode = function(betahat, sebetahat, mixcompdist) {
  z.ash = ash(betahat,sebetahat,mixcompdist = mixcompdist,mode = "estimate")
  average.posteriormean = mean(get_pm(z.ash))
  fitted.mode = comp_mean(get_fitted_g(z.ash))[1]

@@

set.seed(100)
z = rnorm(1000) + 3
print(check_mode(z,1,mixcompdist="uniform"))
print(check_mode(z,1,mixcompdist="normal"))
print(check_mode(z,1,mixcompdist="halfuniform"))
```

@@

  z.ash.hu2 = ash(betahat-0.2,0.1,mixcompdist="halfuniform",outputlevel=4,method="shrink")
  z.ash.pu2 = ash(betahat-0.1,0.1,mixcompdist="+uniform",outputlevel=4,method="shrink")

  z.ash.hu.nzm = ash(betahat,0.1,mixcompdist="halfuniform",mode="estimate",method="shrink")
  z.ash.hu$loglik
  z.ash.hu.nzm$loglik

#  check_mode(betahat,.1,mixcompdist="halfuniform")
```

Note to self: check the normal version works too; check nonzeromodeEMobj  as it doesn't seem needed.

## Session information.

>>>>

```{r evaluate_mode_estimates}
check_mode = function(betahat, sebetahat, mixcompdist) {
  z.ash = ash(betahat,sebetahat,mixcompdist = mixcompdist,mode = "estimate")
  average.posteriormean = mean(get_pm(z.ash))
  fitted.mode           = comp_mean(get_fitted_g(z.ash))[1]

@@

set.seed(100)
z = rnorm(1000) + 3
print(check_mode(z,1,mixcompdist = "uniform"))
print(check_mode(z,1,mixcompdist = "normal"))
print(check_mode(z,1,mixcompdist = "halfuniform"))
```

An additional experiment:

@@

z.ash.hu2    = ash(betahat - 0.2,0.1,mixcompdist = "halfuniform",outputlevel = 4,
                   method = "shrink")
z.ash.pu2    = ash(betahat - 0.1,0.1,mixcompdist = "+uniform",outputlevel = 4,
                   method = "shrink")
z.ash.hu.nzm = ash(betahat,0.1,mixcompdist = "halfuniform",mode = "estimate",
                   method = "shrink")
print(z.ash.hu$loglik,digits = 8)
print(z.ash.hu.nzm$loglik,digits = 8)
```

*Note to self:* check that the normal version works too; check
nonzeromodeEMobj as it doesn't seem needed.

## Session information
